Title

### 2018-08-29 thesis/paper/paper.tex
Improved rules intro

\chapter{Rules}\label{cha_rules}
The previous chapter has show that most constraints cannot be modelled without at least some amount of preprocessing. Only Scope, Conflicts with, Allowed entity types and None of can be modelled directly. This is due to the fact that Conflicts with and None of exclude a limited and specified set of statements from validity and these cases can thus be directly takes as violations. Scope and Allowed entity types work very similar, since there are only three respectively two possible values and violations are simply the options that have not been allowed.  The rules for these constraints are described in section \ref{sec_no_preprocessing}.\\

A problem that occurs multiple times is the need to determine inequality between constants. Distinct value, Allowed units, Allowed qualifiers, One of, Single best value and One-of qualifier value each require a rule to determine if a value, unit or property is not equal to another. To this end a certain amount of preprocessing is necessary, most notably the extraction of all constant pairs whose inequality has to be determined for finding the violations. To avoid putting and undue amount of processing outside of datalog this extraction will not check more than that the constant is in the right position relative to the constrained statement, e.g. all values on statements constrained by Distinct value or all qualifiers on statements constrained by Allowed qualifiers. From this set inequality will be generated, different versions of which will be introduced in section \ref{sec_inequality} and evaluated with regards to their performance in section \ref{sec_inequality_evaluation}.\\

Negation as a general problem cannot be solved in datalog. One could pre-process every necessary fact to be negated and add this to the ground facts, but this is not the purpose of this work. However, not all constraints require a general negation. Item requires statement, Value requires statement, Inverse and Symmetric are all violated if a statement does not exist on a specific item. This problem can be solved with limited amounts of preprocessing by leveraging a preprocessed statement order per item and 'iterating' through the statements until the required conditions are met.\\
A similar approach can be taken to find items with exactly one statement matching certain criteria, required for 	Multi-value. The idea is to ask the question if a second statement exists, then evaluating it as above. Both methods will be explained in section \ref{sec_statement_non-existence}.

>>>>

\chapter{Rules}\label{cha_rules}
The previous chapter has shown that most constraints cannot be modelled without at least some amount of preprocessing. Only \emph{scope}, \emph{conflicts with}, \emph{allowed entity types} and \emph{none of} can be modelled directly. This is due to the fact that \emph{conflicts with} and \emph{none of} exclude a limited and specified set of statements from validity and these cases can thus be directly taken as violations. \emph{scope} and \emph{allowed entity types} work very similar, since there are only three respectively two possible values and violations are simply the options that have not been allowed. The rules for these constraints are described in section \ref{sec_no_preprocessing}.\\

A problem that occurs multiple times is the need to determine inequality between constants. \emph{distinct value}, \emph{allowed units}, \emph{allowed qualifiers}, \emph{one of}, \emph{single best value} and \emph{one-of qualifier value} each require a rule to determine if a value, unit or property is not equal to another. To this end a certain amount of preprocessing is necessary, most notably the extraction of all constant pairs whose inequality has to be determined for finding the violations. To avoid putting and undue amount of processing outside of datalog this extraction will not check more than that the constant is in the right position relative to the constrained statement, e.g., all values on statements constrained by \emph{distinct value} or all qualifiers on statements constrained by \emph{allowed qualifiers}. From this set inequality will be generated, different versions of which will be introduced in section \ref{sec_inequality} and evaluated with regards to their performance in section \ref{sec_inequality_evaluation}.\\

Negation as a general problem cannot be solved in datalog. One could pre-process every necessary fact to be negated and add this to the ground facts, but this is not the purpose of this work. However, not all constraints require a general negation. \emph{item requires statement}, \emph{value requires statement}, \emph{inverse }and \emph{symmetric} are all violated if a statement does not exist on a specific item. This problem can be solved with limited amounts of preprocessing by leveraging a preprocessed statement order per item and 'iterating' through the statements until the required conditions are met.\\
A similar approach can be taken to find items with exactly one statement matching certain criteria, required for 	\emph{multi-value}. The idea is to ask the question if a second statement exists, then evaluating it as above. Both methods will be explained in section \ref{sec_statement_non-existence}.
